Manuscript

### 2014-09-13 inst/simulation/manuscript.Rmd
...

```{r table-1}
ddply(populationSizes, .(Scenario, modelName), function(x) {
  y <- lm(Estimated~Observed, x)
  data.frame(Intercept=round(coef(y)[1], 0), Slope=round(coef(y)[2], 2), R2=round(summary(y)$r.squared, 2))
})
meanPopulationSizes
```

@@

```{r figure-4}
study <- getStudy(scenario="A")
validation <- Validation(study=study)
populationCorrelations <- validation$getValidationSpatialPopulationSizes(modelNames=modelNames[1])

p <- ggplot(populationCorrelations, aes(True, Correlation)) + geom_point(size=1, colour="black") +
  facet_wrap(~Scenario, ncol=2) + xlab("True population size") +
  theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent"))#, axis.text.x=element_text(angle=45, hjust=.5, vjust=1))
print(p)
saveFigure(p, "manuscript-figure-4.png", width=4, height=4)
```

>>>>

```{r table-1a}
x <- ddply(populationSizes, .(Scenario, modelName), function(x) {
  y <- lm(Estimated~Observed, x)
  data.frame(Intercept=round(coef(y)[1], 0), Slope=round(coef(y)[2], 2), R2=round(summary(y)$r.squared, 2))
})
y <- unique(meanPopulationSizes)
join(x, y)
```

```{r table-1b}
x <- ddply(populationSizes2000, .(Scenario, modelName), function(x) {
  y <- lm(Estimated~Observed, x)
  data.frame(Intercept=round(coef(y)[1], 0), Slope=round(coef(y)[2], 2), R2=round(summary(y)$r.squared, 2))
})
y <- unique(meanPopulationSizes2000)
join(x, y)
```

@@

```{r figure-4a}
study <- getStudy(scenario="A")
validation <- Validation(study=study)
populationCorrelations <- validation$getValidationSpatialPopulationSizes(modelNames=modelNames[1])

p <- ggplot(populationCorrelations, aes(True, Correlation)) + geom_point(size=1, colour="black") +
  facet_wrap(~Scenario, ncol=2) + xlab("True population size") +
  theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent"))#, axis.text.x=element_text(angle=45, hjust=.5, vjust=1))
print(p)
saveFigure(p, "manuscript-figure-4a.png", width=4, height=4)
```

```{r figure-4b}
study <- getStudy(scenario="A")
validation <- Validation(study=study)
populationCorrelations <- validation$getValidationSpatialPopulationSizes(scenarios=paste0(scenarios, "combined"), modelNames=modelNames[1])

p <- ggplot(populationCorrelations, aes(True, Correlation)) + geom_point(size=1, colour="black") +
  facet_wrap(~Scenario, ncol=2) + xlab("True population size") +
  theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent"))#, axis.text.x=element_text(angle=45, hjust=.5, vjust=1))
print(p)
saveFigure(p, "manuscript-figure-4b.png", width=4, height=4)
```
